---
title: "SA comparison to constants"
author: "Jessica Furber"
date: "2025-03-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This code is used to compare the constants

```{r load libraries}
library(tidyverse)
library(cowplot)
```

Pull in the csv data from the respective folders - change the path to the appropriate folder (PropFind/Temperature/WaterBodies). Also extracts the values for the water, temperature and prop_find.

```{r import data}
rm(list = ls())

# Get only CSV files that end with "sims.csv"
csv_list_sims <- list.files(
  # path = "Output/SobolIndices/Aedes/Temperature",
  # path = "Output/SobolIndices/Aedes/WaterBodies",
  path = "Output/SobolIndices/Aedes/PropFind",
  pattern = ".csv$", 
  full.names = TRUE
)

# Import the filtered CSV files
csv_imports <- purrr::map_df(csv_list_sims, ~ read_csv(.x, id = "path"))

# Extract the temperature
csv_imports$temperature <- as.numeric(gsub(".*A([0-9]+)temp_.*", "\\1", csv_imports$path))

# Extract the Waterbody
csv_imports$water <- as.numeric(gsub(".*?temp_([0-9]+)wb.*", "\\1", csv_imports$path))

# Extract the Propfind
csv_imports$prop <- as.numeric(gsub(".*?wb_([0-9\\.]+)pf.*", "\\1", csv_imports$path))

# Select relevant columns
csv_imports_temp <- csv_imports %>%
  dplyr::select(parameters, sensitivity, original,temperature)

csv_imports_water <- csv_imports %>%
  dplyr::select(parameters, sensitivity, original,water)

csv_imports_prop <- csv_imports %>%
  dplyr::select(parameters, sensitivity, original,prop)

```

```{r - save to csv to compare  on file}
# write.csv(csv_imports_temp, file = paste0("Output/SobolIndices/Aedes/Temperature/", "Temperature_compare.csv"))
# write.csv(csv_imports_water, file = paste0("Output/SobolIndices/Aedes/WaterBodies/", "Water_compare.csv"))
write.csv(csv_imports_prop, file = paste0("Output/SobolIndices/Aedes/PropFind/", "Prop_compare.csv"))
```


Create plots for each constant parameter. Not all of these will be needed, you can choose which constant parameter you are comparing to plot and then save. This code creates a plot for each one and then saves them all.

```{r}

# Plot for Temperature
plot_temperature <- ggplot(data = csv_imports_temp, aes(x = temperature, y = original, col = parameters)) + 
                    geom_line() + 
                    geom_point() + 
                    facet_wrap(~sensitivity, scales = "free",
                               labeller = labeller(sensitivity = c("Si" = "First Order Index", 
                                                 "Ti" = "Total Effect Index"))) +
                    labs(x = expression("Temperature (" * degree * "C)"),
                         y = "Sobol Sensitivity Index",
                         col = "Parameters") +
                    scale_color_viridis_d(
                      option = "viridis", 
                     labels = c(expression(italic(A[A])), 
                                expression(italic(kappa[A])), 
                                expression(italic(b[A])), 
                                expression(italic(rho[A]^max)))) +
                    scale_x_continuous(breaks = unique(csv_imports_temp$temperature)) +
                    theme_classic()+
                    theme(axis.title = element_text(size = 10),    # Axis labels
                          axis.text = element_text(size = 8),      # Tick labels
                          strip.text = element_text(size = 8),     # Facet titles
                          plot.title = element_text(size = 12)     # Main title) 
                          )

plot_water <- ggplot(data = csv_imports_water, aes(x = water, y = original, col = parameters)) + 
                    geom_line() + 
                    geom_point() + 
                    facet_wrap(~sensitivity, scales = "free",
                               labeller = labeller(sensitivity = c("Si" = "First Order Index", 
                                                 "Ti" = "Total Effect Index"))) +
                    labs(x = expression("Water Body Area (" * m^2 * ")"),
                         y = "Sobol Sensitivity Index",
                         col = "Parameters") +
                    scale_color_viridis_d(
                      option = "viridis", 
                     labels = c(expression(italic(A[A])), 
                                expression(italic(kappa[A])), 
                                expression(italic(b[A])), 
                                expression(italic(rho[A]^max)))) +
                    scale_x_continuous(breaks = unique(csv_imports_water$water)) +
                    theme_classic()+
                    theme(axis.title = element_text(size = 10),    # Axis labels
                          axis.text = element_text(size = 8),      # Tick labels
                          strip.text = element_text(size = 8),     # Facet titles
                          plot.title = element_text(size = 12)     # Main title) 
                          )

plot_prop <- ggplot(data = csv_imports_prop, aes(x = prop, y = original, col = parameters)) + 
                    geom_line() + 
                    geom_point() + 
                    facet_wrap(~sensitivity, scales = "free",
                               labeller = labeller(sensitivity = c("Si" = "First Order Index", 
                                                 "Ti" = "Total Effect Index"))) +
                    labs(x = expression("Detection Probability (" * italic(p[f]) * ")"),
                         y = "Sobol Sensitivity Index",
                         col = "Parameters") +
                    scale_color_viridis_d(
                      option = "viridis",
                     labels = c(expression(italic(A[A])), 
                                expression(italic(kappa[A])), 
                                expression(italic(b[A])), 
                                expression(italic(rho[A]^max)))) +
                    scale_x_continuous(breaks = unique(csv_imports_prop$prop)) +
                    theme_classic()+
                    theme(axis.title = element_text(size = 10),    # Axis labels
                          axis.text = element_text(size = 8),      # Tick labels
                          strip.text = element_text(size = 8),     # Facet titles
                          plot.title = element_text(size = 12)     # Main title) 
                          )

```

Save them all and then move to the appropriate folder before doing the next parameter.

```{r save plot}

ggsave(plot_temperature, filename = "Output/SobolIndices/Aedes/Aedes_temperature.png",
       width = 6, height = 2)
ggsave(plot_temperature,
             filename = "Output/SobolIndices/Aedes/Aedes_temperature.pdf",
             width = 6, height = 2,device=pdf)

ggsave(plot_water, filename = "Output/SobolIndices/Aedes/Aedes_water.png",
       width = 6, height = 2)
ggsave(plot_water,
             filename = "Output/SobolIndices/Aedes/Aedes_water.pdf",
             width = 6, height = 2,device=pdf)

ggsave(plot_prop, filename = "Output/SobolIndices/Aedes/Aedes_prop.png",
       width = 6, height = 2)
ggsave(plot_prop,
             filename = "Output/SobolIndices/Aedes/Aedes_prop.pdf",
             width = 6, height = 2,device=pdf)
```

