---
title: "Sensitivity Analysis"
author: "Sophie North and Jessica Furber"
date: "22/03/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Sensitivity Analysis

## Calculate State Variables

Here we are carrying out a Sobol Sensitivity Analysis, the output of which will be a collection of Sobol indices representing how influential the parameters of interest are on the model output. 

Initially the model will be limited to constant temperature, constant water body area and disease-free scenario, so we are purely looking at how the parameters affect the mosquito abundance and dynamics. 

This code is used to calculate the state variables. The state variables are obtained by running 15 years (15*365 = 5475 days)

Adjust the files SA_SingleSimulation_Culex and SA_SingleSimulation_Aedes to change the state variables to start at 0.

The state variables were just 100 for the egg Culex compartment, and the immature eggs in the Aedes population. I ran this for 5475 days. Then I extracted the compartment sizes at the end of this 2000 day period with a view to input these as the state variables for the actual sensitivity analysis, meaning hopefully the population sizes would stabilise within a short time period.


When calculating the state variables for the periodic case, the state variables are obtained by running  20,000 days (54 years)

```{r rm library source, echo=FALSE}
rm(list = ls())

library(rstudioapi)
library(deSolve)
library(rootSolve)
library(tidyverse)
library(data.table)
library(EnvStats)
library(nimble)
library(sensobol)


```

```{r set general parameters for constants, echo=TRUE}

source("Single_System.R", chdir = TRUE)

SobolSims <<- 9000 # needed to calculate Sobol matrices to find the median
day_length <<- 5475 # initial conditions (15 years for non periodic)
modeloutput <<- "allMozadultsmeanlast28days"
what <<- "one" # one or SA

constanttemp <<- 25 # constant temperature - start mid = 25 degrees C
constantwb <<- 17500 # constant water body area -start  mid = 17,500

```

```{r set general parameters for periodic, echo=TRUE}

source("Single_System_periodic.R", chdir = TRUE)

SobolSims <<- 9000 # needed to calculate Sobol matrices to find the median
day_length <<- 20000 # initial conditions (54 years for periodic)
modeloutput <<- "allMozadultsmeanlast28days"
what <<- "one" # one or SA
```

```{r set constant parameters, echo=TRUE}
livestocktotal <<- 500 
cellarea <<- 1 
prop_find <<- 0.1 # start mid = 10%
```


```{r - set up Sobol matrices and define medians}
#lambda_C = b_C in paper
lambda_C_q <<- "qnorm"; lambda_C_mean <<- 149 ; lambda_C_sd <<- 16.2
#lambda_A = b_A in paper
lambda_A_q <<- "qnorm"; lambda_A_mean <<- 55 ; lambda_A_sd <<- 2.80
#rho_max_C
rho_max_C_q <<- "qunif"; rho_max_C_min <<- 500000 ; rho_max_C_max <<- 20000000
#rho_max_A
rho_max_A_q <<- "qunif"; rho_max_A_min <<- 12000 ; rho_max_A_max <<- 1000000
#A_C
A_C_q <<- "qtri"; A_C_min <<- 196000 ; A_C_max <<- 15904000 ; A_C_mode <<- 9621000 
#A_A
A_A_q <<- "qgamma"; A_A_shape <<- 2.5; A_A_scale <<- 10000
#kappa_C 
kappa_C_q <<- "qunif"; kappa_C_min <<- 0.001 ; kappa_C_max <<- 0.999
#kappa_A
kappa_A_q <<- "qunif"; kappa_A_min <<- 0.001 ; kappa_A_max <<- 0.999



factors_C <<- c("lambda_C", 
                "rho_max_C",
                "A_C", 
                "kappa_C")

factors_A <<- c("lambda_A", 
                "rho_max_A",
                "A_A", 
                "kappa_A")

order <- "first"
sobolmatrix_C <<- sobol_matrices(N=SobolSims/6, params=factors_C, order=order)
sobolmatrix_A <<- sobol_matrices(N=SobolSims/6, params=factors_A, order=order)
samples_C <- sobolmatrix_C
samples_A <- sobolmatrix_A

samples_C[, "lambda_C"] <- 
  match.fun(get(paste0("lambda_C", "_q")))(samples_C[, paste0("lambda_C")],
                                           mean = get(paste0("lambda_C", "_mean")),
                                           sd = get(paste0("lambda_C", "_sd")))

samples_C[, "rho_max_C"] <- 
  match.fun(get(paste0("rho_max_C", "_q")))(samples_C[, paste0("rho_max_C")],
                                            min = get(paste0("rho_max_C", "_min")),
                                            max = get(paste0("rho_max_C", "_max")))

samples_C[, "A_C"] <- 
  match.fun(get(paste0("A_C", "_q")))(samples_C[, paste0("A_C")],
                                      min = get(paste0("A_C", "_min")),
                                      max = get(paste0("A_C", "_max")),
                                      mode = get(paste0("A_C", "_mode")))

samples_C[, "kappa_C"] <- 
  match.fun(get(paste0("kappa_C", "_q")))(samples_C[, paste0("kappa_C")],
                                          min = get(paste0("kappa_C", "_min")),
                                          max = get(paste0("kappa_C", "_max")))
samples_A[, "lambda_A"] <-
  match.fun(get(paste0("lambda_A", "_q")))(samples_A[, paste0("lambda_A")],
                                           mean = get(paste0("lambda_A", "_mean")),
                                           sd = get(paste0("lambda_A", "_sd")))

samples_A[, "rho_max_A"] <-
  match.fun(get(paste0("rho_max_A", "_q")))(samples_A[, paste0("rho_max_A")],
                                            min = get(paste0("rho_max_A", "_min")),
                                            max = get(paste0("rho_max_A", "_max")))

samples_A[, "A_A"] <-
  match.fun(get(paste0("A_A", "_q")))(samples_A[, paste0("A_A")],
                                      shape = get(paste0("A_A", "_shape")),
                                      scale = get(paste0("A_A", "_scale")))

samples_A[, "kappa_A"] <-
  match.fun(get(paste0("kappa_A", "_q")))(samples_A[, paste0("kappa_A")],
                                          min = get(paste0("kappa_A", "_min")),
                                          max = get(paste0("kappa_A", "_max")))

rm(A_A_q, A_A_scale, A_A_shape)
rm(A_C_max, A_C_min, A_C_mode, A_C_q)
rm(kappa_A_max, kappa_A_min,kappa_A_q)
rm(kappa_C_max,kappa_C_min,kappa_C_q)
rm(lambda_A_mean,lambda_A_q,lambda_A_sd)
rm(lambda_C_mean,lambda_C_q,lambda_C_sd)
rm(rho_max_A_max,rho_max_A_min,rho_max_A_q)
rm(rho_max_C_max,rho_max_C_min,rho_max_C_q)

rm(sobolmatrix_A,sobolmatrix_C)


lambda_C_med <<- median(samples_C[, "lambda_C"])
lambda_A_med <<- median(samples_A[, "lambda_A"])
rho_max_C_med <<- median(samples_C[, "rho_max_C"])
rho_max_A_med <<- median(samples_A[, "rho_max_A"])
kappa_C_med <<- median(samples_C[, "kappa_C"])
kappa_A_med <<- median(samples_A[, "kappa_A"])
A_C_med <<- median(samples_C[, "A_C"])
A_A_med <<- median(samples_A[, "A_A"])

lambda_A <- lambda_A_med
rho_max_A <- rho_max_A_med
kappa_A <- kappa_A_med
A_A <- A_A_med

# these values used in the paper
# lambda_A <<- 100
# rho_max_A <<- 1.5E5
# kappa_A <<- 0.001
# A_A <<- 1E6

lambda_C <- lambda_C_med
rho_max_C <- rho_max_C_med
kappa_C <- kappa_C_med
A_C <- A_C_med

# these values used in the paper
# lambda_C <- 200
# rho_max_C <- 1.5E5
# kappa_C <- 0.001
# A_C <- 1E6

rm(lambda_C_med,lambda_A_med,rho_max_A_med,rho_max_C_med,kappa_C_med,kappa_A_med,A_C_med,A_A_med)

```

We model each mosquito separately, so estimate population separately. A csv file is automatically saved.

```{r single sim for Culex gauging numbers and finding state variables, eval = FALSE}
singleSim_OnlyCulex(lambda_C,
               rho_max_C,
               A_C,
               kappa_C )
```

```{r single sim for Aedes gauging numbers and finding state variables, eval = FALSE}

singleSim_OnlyAedes(lambda_A,
               rho_max_A,
               A_A,
               kappa_A )

```


To view the numbers at time 5475 for each population in R:(to view at 20,000, change value)

```{r import state variable table}
culex_state_variables <- read.csv("Output/SobolIndices/Culex/State_Variables/Culex_SingleSim.csv")
culex_state_variables <- culex_state_variables %>%
  dplyr::filter(Time == 5475)
culex_state_variables <- culex_state_variables %>%
  dplyr::select(-1)
head(culex_state_variables)
```

```{r import state variable table}
aedes_state_variables <- read.csv("Output/SobolIndices/Aedes/State_Variables/Aedes_SingleSim.csv")
aedes_state_variables <- aedes_state_variables %>%
  dplyr::filter(Time == 5475)
aedes_state_variables <- aedes_state_variables %>%
  dplyr::select(-1)
head(aedes_state_variables)
```
